Proportional multi-state multiple-cohort life table model

### 2018-04-24 MSLT/MSLTdoc.Rmd
Updated DWs

  geom_line(mapping = aes(y = total_inc_num_bl_ihd, colour = "total_mx_num_bl_ihd")) +
  theme_classic() +
  geom_hline(yintercept=0, linetype="dashed", color = "black") +
  geom_line(mapping = aes(y = total_inc_num_sc_ihd, colour = "total_mx_num_sc_ihd")) +
  geom_line(mapping = aes(y = total_inc_num_diff_ihd, colour = "total_mx_num_diff_ihd")) +
  xlab ("Simulation years") + ylab ("Cases") + labs (title = paste(disease_outcome)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  scale_color_discrete(name = paste(""), labels = c("Baseline", "Scenario", "Difference")) +
  theme(plot.title = element_text(hjust = 0.5))

>>>>

  geom_line(mapping = aes(y = total_inc_num_bl_ihd, colour = "total_mx_num_bl_ihd")) +
  theme_classic() +
  geom_hline(yintercept=0, linetype="dashed", color = "black") +
  geom_line(mapping = aes(y = total_inc_num_sc_ihd, colour = "total_mx_num_sc_ihd")) +
  geom_line(mapping = aes(y = total_inc_num_diff_ihd, colour = "total_mx_num_diff_ihd")) +
  xlab ("Simulation years") + ylab ("Cases") + labs (title = paste(disease_outcome)) +
  theme(plot.title = element_text(hjust = 0.5, size = 12)) +
  scale_color_discrete(name = paste(""), labels = c("Baseline", "Difference", "Scenario")) +
  theme(plot.title = element_text(hjust = 0.5))
